<header style="text-align: center">

### 2019-05-22 report/report.Rmd
Hide title and subtitle from sidebar toc

---
title: '<header style="text-align: center">
			<h1 style="font-weight: bold; font-size: 44px">2016 Brussels Bombings</h1>
			<h2>Air Traffic Analysis</h2>
		</header>'
author: '<div style="text-align: center">
			<span style="display: inline-block; width: 30%; margin: 0 5px">[Ramiro Balado Ordax](https://github.com/Qjammer)</span>
			<span style="display: inline-block; width: 30%; margin: 0 5px">[Alejandro Hernández Rubio](https://github.com/Shyryuu)</span>
			<span style="display: inline-block; width: 30%; margin: 0 5px">[Pol Mesalles Ripoll](https://github.com/polmes)</span>
		</div>'
# date: "DD/MM/YYYY"
output:
    rmarkdown::html_document:
        theme: cosmo
        highlight: tango
        number_sections: true
        toc: true
        toc_float: true
---

>>>>

---
title: '<header style="text-align: center">
			<h1 style="font-weight: bold; font-size: 44px" class="toc-ignore">2016 Brussels Bombings</h1>
			<h2 class="toc-ignore">Air Traffic Analysis</h2>
		</header>'
author: '<div style="text-align: center">
			<span style="display: inline-block; width: 30%; margin: 0 5px">[Ramiro Balado Ordax](https://github.com/Qjammer)</span>
			<span style="display: inline-block; width: 30%; margin: 0 5px">[Alejandro Hernández Rubio](https://github.com/Shyryuu)</span>
			<span style="display: inline-block; width: 30%; margin: 0 5px">[Pol Mesalles Ripoll](https://github.com/polmes)</span>
		</div>'
# date: "DD/MM/YYYY"
output:
    rmarkdown::html_document:
        theme: cosmo
        highlight: tango
        number_sections: true
        toc: true
        toc_float: true
---
